CODE CHECK

### 2020-09-15 codecheck-paper.Rmd
push

* Can we switch to latex for this?  (Find it slightly easier.)
* Which journal to target -- maybe worry abotu that once we have a
  preprint.  F1000R my current favourite?

@@

Figure 1: the inverse problem figure.

@@

Figure 2: the detective.  Could we number the arrows as steps?
(Implementing the CODECHECK process)

@@

All the related projectsfrom A-Z... e.g. CASCAID, Rescience, modeldb,
o2r,

@@

@@

- untilhe co modelDB principle.

@@

@@

- eLife
- GigaScience
- AH, SciData
- Mozilla
- PLOS?
- Richard van Noorden, Dalmeet Singh (paper 9)
- Iain Davies and Sebastian 
- SSI for some funding.

>>>>

* Prefer longlines or short?
* Can we switch to latex for this?  (Find it slightly easier.)
* Which journal to target -- maybe worry abotu that once we have a
  preprint.  F1000R my current favourite?

* Check with Giuliano re: "code works".

@@

\begin{figure}
  \centering
  \includegraphics{figs/rr.pdf}
  \caption{The inverse problem in reproducible research.  The left
  half of the diagram shows the diverse range of materials used
  internally within a laboratory.  These materials are often then
  condensed into a paper for sharing with the outside world via the
  research paper, astatic PDF document.  Working backwards from the
  PDF to the underlying materials is impossible.  By sharing the
  materials on the left, others outside the lab are able to reproduce
  or build on this work.  (Should we draw a backward arrow showing the
  impossibility of this backward flow?)}
  \label{fig:inverse}
\end{figure}

@@

\begin{figure}
  \centering
  \caption{The detective. Could we number the arrows as steps?
(Implementing the CODECHECK process).  DANIEL: best source for this figure?}
  \label{fig:worfklow}
\end{figure}

@@

All the related projectsfrom A-Z... e.g. CASCAID, Rescience, modeldb,
o2r.  Community iniatives like reprohack along similar lines of
checking code. <https://reprohack.github.io/reprohack-hq/>

@@

Handling failure:  we have no established process for this, as so far
all our codechecks succeeded.  Open question remains as what to do in
this case -- should we publicly report that the code would not run.

@@

- modelDB principle: minimum of one figure should be reproducibe.
  Exampler certificate 2020-016 (I think) which had only a small
  subset of the possible figures.  Still useful and worth sharing.

@@

# Declaration of interest

SJE is on the senior editorial board at the journal *Scientific Data*.

@@

We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison, Giuliano
Maciocci (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (Gigascience) Andrew Hufton (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang worked on developing code and example
certificates.  This work was financially supported by the UK Software
Sustainability Institute and a Mozilla Science mini grant.
